Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas

### 2021-04-10 analysis/paper/paper.Rmd
UPDATE NAMES IN ACKNOWLEDGEMENTS

We recognize that the species and ecosystems studied in this paper are within the
traditional range of the Inpuiaq and Yupik people. And, we would like to acknowledge and
thank them as the original stewards of these ecosystems. The deployment of bio-logging
devices used in this study were often done in collaboration with Alaska Native
communities. We would like to especially acknowledge the communities of Kotzebue,
Utqiagvik, and Ulguniq and the following individuals: James Adams, Jeff Barger, David
Barr, Wendell Booth, Tom Jones, Frank Garfield, Brenda Goodwin, Henry Goodwin, John
Goodwin, Pearl Goodwin, Willie Goodwin, Brett Kirk, Noah Naylor, Virgil Naylor Jr., Virgil
Naylor Sr., Dan Savetilik, Allen Stone, and Randy Toshavik from Kotzebue, Alaska; Billy
Adams, Mary-Ellen Ahmaogak, James Aiken, Tim Aiken, Sarah Coburn, Jason Herreman, Howard
Kittick, Gilbert Leavitt, Isaac Leavitt, J.R. Leavitt, Enoch Oktollik, Shawn Oktollik,
Stacey Osborn, Fred Rexford, Chuck Schaeffer, Ross Schaeffer, Bob Shears, and Joe Skin
from the North Slope Borough, Alaska;

>>>>

We recognize that the species and ecosystems studied in this paper are within the
traditional range of the Inpuiaq and Yupik people. And, we would like to acknowledge and
thank them as the original stewards of these ecosystems. The deployment of bio-logging
devices used in this study were often done in collaboration with Alaska Native
communities. We would like to especially acknowledge the communities of Kotzebue,
Utqiagvik, and Ulguniq and the following individuals: James Adams, Jeff Barger, David
Barr, Wendell Booth, Cyrus Harris, Nereus 'Doc' Harris, Grover Harris, Lee Harris, Tom
Jones, Frank Garfield, Brenda Goodwin, Henry Goodwin, John Goodwin, Pearl Goodwin, Willie
Goodwin, Brett Kirk, Noah Naylor, Virgil Naylor Jr., Virgil Naylor Sr., Dan Savetilik,
Allen Stone, and Randy Toshavik from Kotzebue, Alaska; Billy Adams, Mary-Ellen Ahmaogak,
James Aiken, Tim Aiken, Sarah Coburn, Jason Herreman, Howard Kittick, Gilbert Leavitt,
Isaac Leavitt, J.R. Leavitt, Enoch Oktollik, Shawn Oktollik, Stacey Osborn, Fred Rexford,
Chuck Schaeffer, Ross Schaeffer, Bob Shears, and Joe Skin from the North Slope Borough,
Alaska;
